Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-10-18 fib2.tex
more words

We give an informal introduction to
the easy (picture) topological quantum
field theory in $(2+1)$-dimensions.
Note that these theories give rise to
\emph{doubled} anyonic charges, and so
the example in the main text only simulates
one half of such a system...

\section{Interaction picture}

@@

Braid group acts (naturally) on states.

@@

>>>>

The goal here is to describe the algorithm for
computing charge contained regions built from 
arbitrary collection of tiles.
To do this we first describe our approach
to topological quantum field theory,
then we discuss the data structure 
(combinatorial curve diagrams) and the algorithm
that operates on these structures.

We give an informal introduction to
anyonic topological quantum
field theory in $(2+1)$-dimensions.
See \cite{beverland2014} for a similar treatment.
Note that these theories give rise to
\emph{doubled} anyonic charges, and so
the Fibonacci example in the main text simulates
one half of such a system.

%\section{Interaction picture}
\section{Topological quantum field theory}

@@

%Braid group acts (naturally) on states.

@@

%This discussion makes it clear we have picked out a
%specific curve $c$ that we use as a reference point for
%other curves.

The importance of this isomorphism: the simulation
algorithm calculates outcomes of observations. This
boils down to a change of basis, to one that includes
the required observable.
$F$-moves allow us to re-assocate observables along
a curve diagram. The mapping class group acts
transitively on curve diagrams (\emph{why??}).
